Clique and Constraint Models for Maximum Common (Connected) Subgraph Problems

### 2016-04-20 paper/paper.tex
Clarify
No the

A closer inspection of the data suggests that the different randomness models have little effect on
the runtimes for either approach. However, the relative size of the solution matters, particularly
for the clique algorithm: if the solution is large (i.e.\ the two input graphs are very similar),
the clique approach finds nearly every labelled instance trivial.

@@

In many applications, the common subgraph must be connected
\cite{DBLP:journals/tcs/Koch01,DBLP:journals/jcamd/RaymondW02a,DBLP:conf/mco/VismaraV08,Ehrlich:2011}.
Adding the connectedness requirement makes certain special cases solvable in polynomial time,
including outerplanar graphs of bounded degree \cite{DBLP:journals/algorithms/AkutsuT13} and trees
\cite{DBLP:journals/corr/DroschinskyKM16}, but the general case remains \NP-hard. As illustrated in
\cref{figure:mcsexample}, the MCCS cannot be deduced from the MCS: we need to ensure connectedness
during the search. In \cref{mccs-cp}, we show that in CP this may be done in two different ways that
may be combined, and we show in \cref{mccs-cp-eval} that the best results are obtained when
combining them. In \cref{mccs-clique}, we introduce a new way for ensuring connectedness in a
clique-based approach. Finally, we compare CP and our clique-based approach in \cref{mccs-eval}.

>>>>

A closer inspection of the data suggests that the different randomness models used to generate
instances have little effect on the runtimes for either approach. However, the relative size of the
solution matters, particularly for the clique algorithm: if the solution is large (i.e.\ the two
input graphs are very similar), the clique approach finds nearly every labelled instance trivial.

@@

In many applications, the common subgraph must be connected
\cite{DBLP:journals/tcs/Koch01,DBLP:journals/jcamd/RaymondW02a,DBLP:conf/mco/VismaraV08,Ehrlich:2011}.
Adding the connectedness requirement makes certain special cases solvable in polynomial time,
including outerplanar graphs of bounded degree \cite{DBLP:journals/algorithms/AkutsuT13} and trees
\cite{DBLP:journals/corr/DroschinskyKM16}, but the general case remains \NP-hard. As illustrated in
\cref{figure:mcsexample}, the MCCS cannot be deduced from the MCS: we need to ensure connectedness
during search. In \cref{mccs-cp}, we show that in CP this may be done in two different ways that
may be combined, and we show in \cref{mccs-cp-eval} that the best results are obtained when
combining them. In \cref{mccs-clique}, we introduce a new way for ensuring connectedness in a
clique-based approach. Finally, we compare CP and our clique-based approach in \cref{mccs-eval}.
